---
title: "R you serious?"
subtitle: "Draft 1"
author: "Torkil Rogneflåten"
editor_options:
  chunk_output_type: console
bibliography: resources/references.bib
csl: resources/apa.csl
format: pdf
---

```{r}
#| include: false


library(tidyverse)
library(readxl)

```


# R you kidding me?

This is a text. It explains something important. Combining `code` and text with Quarto is ...

R you sure that R is best? Read @wickham2017r book on R and data science to find out for yourself.


## Showing of R code and output

In the `sim-rawdata.R` file I made a dataset with the following code:

```{r}
#| echo: true

# simulating a dataset
rawdata <- data.frame(y = rnorm(100, mean = 5, sd = 2),
                      z = rnorm(100, mean = 10, sd = 3))
```

This is a snippet of what the dataset looks like:

```{r}
#| echo: false

data <- read_excel("data/raw-data/rawdata.xlsx")

head(data)


```

\newpage

This is a "detailed" plot of the data with all t-test info of statistical differences between y and z.

```{r}
#| fig-cap: "**Figure 1**. This is a figure. Grey points indicates individual values. Red crossline indicates the group average value."
#| fig-subcap: ""
#| fig-cap-location: bottom
#| fig-width: 5.5
#| fig-height: 4.5
#| fig-dpi: 600
#| fig-align: "center"
#| echo: false

figure1 <- readRDS("./figures/figure1.RDS")

figure1
```



# References {.unnumbered}

